Exploration

### 2018-03-06 exploration.Rmd
confirmed operations, vectorized a bit more

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p$p_emig*p.ij, ~(Fb[z.i,z.i,.x] * .y)))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + Fb[1,z.i,sdd.j] %*% (p$p_emig*p.ij)

  #---- generate data: add immigrants
  # total immigrants
  D[i] <- sum(sdd[,,3,][sdd[,,2,]==sdd.i])
  # seed bank: immigrants
  B_1[i] <- B_1[i] + D[i] * (1 - p$rcr_dir) * p$s_SB
  # recruits: immigrants
  rcr.imm <- max(ceiling(D[i] * p$rcr_dir * p$p_est), 2)
  rcr.i <- (1:rcr.imm) + nrow(d[[i]])
  d[[i]][rcr.i,] <- NA
  d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.imm, p$rcr_z[1], p$rcr_z[2])
}
IPMs <- Ps + Fs
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% add_column(nSd=nSd, B0=B, B1=B_1, D=D)

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=B1>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*p$p_emig > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)

>>>>

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)
  p.ij <- sdd[,,1,][sdd.j]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    h * Reduce(`+`, map2(sdd.j[,3], p$p_emig*p.ij, ~(Fb[z.i,z.i,.x] * .y)))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + Fb[1,z.i,sdd.j[,3]] %*% (p$p_emig*p.ij)

  #---- generate data: add immigrants
  # total immigrants
  D[i] <- sum(sdd[,,3,][sdd.j])
  # seed bank: immigrants
  B_1[i] <- B_1[i] + D[i] * (1 - p$rcr_dir) * p$s_SB
  # recruits: immigrants
  rcr.imm <- max(ceiling(D[i] * p$rcr_dir * p$p_est), 2)
  rcr.i <- (1:rcr.imm) + nrow(d[[i]])
  d[[i]][rcr.i,] <- NA
  d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.imm, p$rcr_z[1], p$rcr_z[2])
}
IPMs <- Ps + Fs
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% add_column(nSd=nSd, B0=B, B1=B_1, D=D) %>%
  mutate(nSdStay=nSd*(1-p$p_emig), nSdLeave=nSd*p$p_emig)

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=B1>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=(D-nSdStay)/nSdStay)) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSdStay < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)
